\huge Metamorphic Testing in Cross-language Sentiment Analysis for Social Media

### 2018-09-05 submit/paper.tex
backup

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tabularx}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{\huge Metamorphic Testing in Cross-language Sentiment Analysis for Social Media}

@@

\begin{abstract}
  There are huge amount of text comments for discussion different topics in Social
  Media everday. All of those topics have discusse by different language
  spearkers. Most of people have language and culture barrier when we doing
  cross-language communicate with each other. However, cross-language opinion
  mining is useful for global integration. However, most of researches only fouced on
  English Sentiment Analysis. In this research, using machine
  trainslation and sentiment analysis tools to solve this problems. Let people
  can understand different language speakers' attitudes (positive or negative),
  emotions and opinions. It is based on Metamorphic Testing method to achieve a
  testing model for finding which machine translator service combined with which
  English sentiment analysis service can obtain reliable sentiment analysis
  result for non-English speaker, who does not have sentiment analysis tool to
  analysis their own language. As a result, people can use Machine Translation
  and English Sentiment Analysis doing big data analysis in Social Media.
\end{abstract}

@@

Social Media has been becoming more and more widely used. There are lots of text comments
on different discussion topics every day.
It would be impossible to analyses the huge amount of data generated manually.
These topics are discussed by speakers of different languages, from different
cultural backgrounds, further complicating any analysis.
Most people enounter language and cultureal barriers during cross-language
communication.
In this paper, the use of machine translation and sentiment analysis tools to
solve this problem of analysing cross-cultural and cross-language data is
explored and discussed.
Sentiment analysis is a part of text data mining. The aim of sentiment analysis
is to determine the attitude of speakers or writers with respect to particular topics
or the overall contextual polarity or emotional reaction to a text document. It is usually equated with
opinion mining, which involves the use of natural language processing and
machine learning to ascertain the possibility of positive or negative opinions \cite{sentimentAnalysis}.
Sentiment analysis is useful for analyzing a huge amount of data relating to personal
opinions. It can be used in an e-business context. For example, business managers can analysise
customers' attitudes, as to whether they like or dislike their product or service.
Also, government can use sentiment analysis to analyze citizen perspectives.
In a word, sentiment analysis is coming into widespread use.
As Dr. Haiyun mentions, English language sentiment analysis research has
undergone major developments in recent years \cite{ChineseSentimentAnalysis}.
However, less research has been undertaken in other languages, such as Chinese.
Today, a lot of English language sentiment analysis theories have been
developed. Also, a variety of Machine Translation tools is available, such as Google
translation, Bing translation and Yandex translation.
Manchine Translation uses computational linguistic programs and natural language
processing theory \cite{machineTranslation}.
However, nobody working in a combination of these two fields of research has undertaken non-English
sentiment analysis. Therefore, the research described and discussed in this paper aims to create a testing model to find the best-combination of English
sentiment analysis tools and machine translation tools to obtain reliable
sentiment analysis results from non-English texts, for non-English speakers who
do not have such sentiment analysis tools to analyze their own language.
Eventually, everyone will be able to understand different language speakers'
attitudes (positive or negative), emotions and opinions.\\
\section{Part A: Annotated bibliography}
\nocite{*}
\bibliographystyle{annotate}
\bibliography{library}
\section{Literature Review}
This research consists of three components; measuring machine translation
service quality; testing sentiment analysis service quality;
finding the best compound mode for machine translation service and
sentiment analysis service.
As a result, this section will focus on a review of literature review about machine
translation, Testing methodology and sentiment analysis.
\subsection{Testing in Machine translation}
There are two research articles about testing modeling of machine
translation(MT).

@@

There is a research article written by Zhou in 2016. This article is
well-explained for what is Metamorphic Testing.
As Zhou said, Metamorphic Testing (MT) is a property-based software testing

@@

relations among the inputs and outcomes of multiple executions of the target

@@

For instance, test calculator function correctness will be shown if input 1 + 1,
and the result will be 2. In this example people can easily make the judgment,
is correct or not.
However, people will not easly make this judgment quickly if input sin (3.7),
and the calculator gives an output.

@@

\section{Research Proposal}\footnote{This research proposal is based on Boyang
  Yan's Master of Research application (research proposal section) in 2017}
TITLE: Metamorphic Testing in Cross-language Sentiment Analysis for Social Media
\paragraph{Background and Research Problems}

@@

\paragraph{Critical Review of Literature}

\paragraph{Aims and Objectives}
The aim for this research is to achieve a method to find out which combination
between machine translation tools and English sentiment analysis model can
obtain the result, which is the most reliable and efficient, for those
non-English speakers, to fill the blank and gap of lacking of cross-language
sentiment analysis tool.
The main aim can be divided into 4 sub-aims.
\begin{enumerate}
  \item Advertisement Detection \\
Detect advertisements and junk contents among mass of data from social media
texts. Removing unimportant data can both reduce the amount of the size of whole
dataset to save processing time, and get rid of contents that is of no use to
our sentiment analysis, which can be also regarded as noise data.
  \item Data Preprocessing and Feature Extraction
Preprocessing data is to segment texts into words and select those words which
is helpful and sensitive in sentiment analysis. E.g. keywords, important
punctuation marks, emotion symbols. Also, normalization operations will be taken
to convert the keywords into it root form, which can reduce the size of lexicons
of models to a large extend. Then, extracting features of those data being
preprocessed as inputs for sentiment analysis model built by us.
  \item Sentiment Analysis Modelling
Develop a model for sentiment analysis which includes a lexicon placing emphasis on social media texts and a machine learning model for analyzing sentiment.
The lexicon should consider about the main feature of social media texts below:
short-text styled, sparsity of contents and concluding emoticons. This can make
our model performs better than the other ones which focus on general texts.
For the machine learning model, we aim to design a model which considers about
efficiency, accuracy and reliability.
  \item Cross-language Translation and Model Testing
For our source of data coming from social media which is in different languages,
finding a better performed tool for translation is of vital importance. We aim
to find the best performed tool for each respective combination of languages, so
that we can have closer meaning according to the origin language.

@@

\section{Survey - Questionnaire}

@@

    \item Are you willing to try to understand a comment in an unknown language ?
    \begin{enumerate}
        \item Very likely
        \item Likely
        \item Neither likely nor likely
        \item Unlikely
        \item Very unlikely
    \end{enumerate}
    \textit{Initial Code : Behavior towards unknown languages}

\begin{enumerate}
\item What is your gender? \\
  O Male O Female O perfer Not to say
\item What is your age group? \\
  O <18ys O 18-24ys O 24-30ys O 30-40ys O 40-50ys O >50ys
\item What are your areas of interest? (many answers possible) \\
  O Science and Technology O engineering O entertainment O military O politics O
  law O literature O Other (please specify) .....................
\item How often do you use social media ?\\
  O Hourly O Daily O Weekly O monthly O yearly
\item How long do you use social media each time? \\
  O time >= 1 hour O time 30 minutes O 1 hour O 10 minutes to 30 minutes O less than 10 minutes
\item Which social media platforms do you use regularly ? (many answers possible)\\
  O Facebook O Twitter O YouTube O Instagram O WeChat O LinkedIn O Weibo O I
  don't use social media O Other (please specify)
\item Which language(s) can you understand easily ?\\
  O English O French O Chinese O Spanish O Vietnamese O Arabic O Indian O
  Russian O German O Other (please specify)
\item How interested are you in other culture? \\
  O Extremely interested O Very interested O Somewhat interested O Not so
  interested O Not at all interested
\item How willing are you to understand the contents in an foreign language?\\
  O Very likely O Likely O Neither likely nor unlikely O Unlikely O Very
  unlikely

\item How often do you read others' opinion ?\\
  O Always O Usually O Sometimes O Rarely O Never

\item Which machine translation tool do you use most?\\
  O Google Translation O Microsoft Bing Translation O Yandex Translation O Baidu
  Translation O Youdao Translation O Other (please specify) .......
\item Sentiment analysis tool can determine the attitude (positive or negative)
  of writers, which can be useful for analyzing a huge amount of comments. Are
  you willing to use this tool to analyze your interests in social
  media, such as product comments or restaurant review, etc?\\
  O Very likely O Likely O Neither likely nor unlikely O Unlikely O Very unlikely
\end{enumerate}
\bibliographystyle{IEEEtran}
\bibliography{library}
\end{document}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{adjustbox}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tabularx}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{\huge Metamorphic Testing in Cross-language Sentiment Analysis for Social Media}

@@

\begin{abstract}
  Huge amounts of text comments are posted on different topics in Social
  Media everday. These topics are discussed in different languages by different language
  speakers. Most people encounter language and culture barriers when engaging in
  cross-language communication. Cross-language opinion
  mining is useful for global integration. However, most research only focuses on
  English language sentiment analysis, but little research has been conducted on
  sentiment analysis in languages other than English. This research explores using machine
  trainslation and sentiment analysis tools to fill this gap. The research
  identifies a conbination of tools which will enable people to understand different language speakers' attitudes (positive or negative),
  emotions and opinions. This research is  based on the Metamorphic Testing method to establish a
  testing model for finding which machine translator service combined with which
  English sentiment analysis service can obtain reliable sentiment analysis
  results for non-English speakers who do not have sentiment analysis tools to
  analysis their own language. As a result, people will able to use Machine Translation
  and English Sentiment Analysis to conduct big data analysis in multi-language Social Media.
\end{abstract}

@@

Social Media has been becoming more and more widely used. There are lots of text comments
on different discussion topics every day.
It would be impossible to analyses the huge amount of data generated manually.
These topics are discussed by speakers of different languages, from different
cultural backgrounds, further complicating any analysis.
Most people enounter language and cultureal barriers during cross-language
communication.
In this paper, the use of machine translation and sentiment analysis tools to
solve this problem of analysing cross-cultural and cross-language data is
explored and discussed.
Sentiment analysis is a part of text data mining. The aim of sentiment analysis
is to determine the attitude of speakers or writers with respect to particular topics
or the overall contextual polarity or emotional reaction to a text document. It is usually equated with
opinion mining, which involves the use of natural language processing and
machine learning to ascertain the possibility of positive or negative opinions \cite{sentimentAnalysis}.
Sentiment analysis is useful for analyzing a huge amount of data relating to personal
opinions. It can be used in an e-business context. For example, business managers can analysise
customers' attitudes, as to whether they like or dislike their product or service.
Also, government can use sentiment analysis to analyze citizen perspectives.
In a word, sentiment analysis is coming into widespread use.
As Dr. Haiyun mentions, English language sentiment analysis research has
undergone major developments in recent years \cite{ChineseSentimentAnalysis}.
However, less research has been undertaken in other languages, such as Chinese.
Today, a lot of English language sentiment analysis theories have been
developed. Also, a variety of Machine Translation tools is available, such as Google
translation, Bing translation and Yandex translation.
Manchine Translation uses computational linguistic programs and natural language
processing theory \cite{machineTranslation}.
However, nobody working in a combination of these two fields of research has undertaken non-English
sentiment analysis. Therefore, the research described and discussed in this paper aims to create a testing model to find the best-combination of English
sentiment analysis tools and machine translation tools to obtain reliable
sentiment analysis results from non-English texts, for non-English speakers who
do not have such sentiment analysis tools to analyze their own language.
Eventually, everyone will be able to understand different language speakers'
attitudes (positive or negative), emotions and opinions.\\
\section{Part A: Annotated bibliography}

\section{Literature Review}
This research consists of three components; measuring machine translation
service quality; testing sentiment analysis service quality;
finding the best compound mode for machine translation service and
sentiment analysis service.
As a result, this section will focus on a review of literature review about machine
translation, Testing methodology and sentiment analysis.
\subsection{Testing in Machine translation}
There are two research articles about testing modeling of machine
translation(MT).

@@

A research article written by Zhou in 2016 clearly explains what Metamorphic
Testing is.
As Zhou explains, Metamorphic Testing (MT) is a property-based software testing

@@

relations between the inputs and outcomes of multiple executions of the target

@@

For instance, calculator function correctness will be established if the input is 1 + 1,
and the result is 2. In this example people can easily make the judgment,
whether the calculator is functioning correctly or not.
However, people will not be able to easily make this judgment if the input is sin (3.7).

@@

\pagebreak
\pagebreak
\section{Research Proposal \protect\footnote{This research proposal is based on
    Boyang Yan's Master of Research application (research proposal section) in
    2017}}
\subsection{TITLE}
Metamorphic Testing in Cross-language Sentiment Analysis for Social Media
\subsection{Background and Research Problems}

@@

\subsection{Critical Review of Literature}

\subsection{Aims and Objectives}
The aim for this research is to achieve a method to find out the combination
between machine translation tools and English sentiment analysis model can
obtain the result, which is the most reliable and efficient, for those
non-English speakers, to fill the blank and gap of lacking of cross-language
sentiment analysis tool.
The main aim can be divided into 4 sub-aims.
\begin{enumerate}
  \item Advertisement Detection \\
Detect advertisements and junk contents among mass of data from social media
texts. Removing unimportant data can both reduce the amount of the size of whole
dataset to save processing time, and get rid of contents that is of no use to
our sentiment analysis, which can be also regarded as noise data.
  \item Data Preprocessing and Feature Extraction \\
Preprocessing data is to segment texts into words and select those words which
is helpful and sensitive in sentiment analysis. E.g. keywords, important
punctuation marks, emotion symbols. Also, normalization operations will be taken
to convert the keywords into it root form, which can reduce the size of lexicons
of models to a large extend. Then, extracting features of those data being
preprocessed as inputs for sentiment analysis model built by us.
  \item Sentiment Analysis Modelling \\
Develop a model for sentiment analysis which includes a lexicon placing emphasis on social media texts and a machine learning model for analyzing sentiment.
The lexicon should consider about the main feature of social media texts below:
short-text styled, sparsity of contents and concluding emoticons. This can make
our model performs better than the other ones which focus on general texts.
For the machine learning model, we aim to design a model which considers about
efficiency, accuracy and reliability.
  \item Cross-language Translation and Model Testing \\
For our source of data coming from social media which is in different languages,
finding a better performed tool for translation is of vital importance. We aim
to find the best performed tool for each respective combination of languages, so
that we can have closer meaning according to the origin language.

@@

\subsection{The procedure of the study}
\begin{enumerate}
\item {Survey} \\
  The research conducts a survey to different languages backgrounds people,
  about what they thinking about globalization, does they want to know different
  cultural backgrounds people opinions and attitudes. Does they enounter language and cultureal barriers during cross-language
communication. The purpose of survey is Machine Translation tools and Sentiment
analysis Tools are useful for people daily life and established connection
between different cultural people communication.
\item{Getting test data}\\
  if in the survey, we can get most of people enounter language and
  cultureal barriers and insterest in others culture, we can start getting movie
  reviews data from social media website for finding the best compound mode for machine translation service and
  sentiment analysis services

\item Testing Machine translation services quality and Sentiment Analysis
  services quality \\
  In this part fouce on testing Yandex, Baidu, Google Machine Translation tools,
  as well as, Baidu, Google sentiment analysis tools. This is testing model,
  which is according to Metamorphic Testing Method.
  \begin{minipage}[t]{\linewidth}
          \raggedright
          \adjustbox{valign=t}{%
            \includegraphics[width=.8\linewidth]{./img/testingModel.png}%
          }
          \medskip
  \end{minipage}
When we testing Machine Translation. We need assuming sentiment analysis tools
are profect correct. We can compare correlation coefficient between both side of
sentiment analysis results for getting which machine translation are better.
There is an example for testing Chinese to English machine translation.
\begin{enumerate}
  \item Using Google, Baidu, Yandex translation tools, translated original Chinese data to English data
  \item Using same sentiment analysis tool analysis original chinese dataset and
    translated dataset
  \item Calculate correlation coefficient between Chinese sentiment analysis
    results and English sentiment analysis results
  \item Compare correlation coefficient values. if value is bigger than others,
    we can say this translation tool, which use in original dataset to English
    dataset, can achieve better results than others.
  \end{enumerate}
For testing sentiment analysis tools, we can using same model. We need assuming
Machine Translation tools are profect correct. If right side of sentiment
analysis result is opposite attitude with left side of sentiment analysis
result. We can say we are detected one failure.
\item {Finding the best compound mode for machine translation service and
    sentiment analysis services} \\
  In this part, we totally have 6 kinds of compound model, which are Google
  translation with Google sentiment analysis; Yandex translation with Google
  sentiment analysis; Baidu translation with Google sentiment analysis; Google
  translation with Baidu sentiment analysis; Yandex translation with Baidu
  sentiment analysis and Baidu translation with Baidu sentiment analysis. we can
  using mean-square error (MSE) and Receiver operating characteristic (ROC)
  compare with user rate get the best compound model.
\item {Create own sentiment analysis model} \\
  Accounting to Liu said, creating sentiment analysis model have five steps. I will basis
  on this five steps for create my own model \cite{liu2012survey}.
  \begin{enumerate}
    \item{GetTerms - Reduce review to the list of keywords}
    \item{Filtering - Remove unnecessary keywords that will not add value for
        sentiment analysis, such as is, but, it etc}
    \item{Find the Base Word - Convert all inflections to their root word}
    \item{Make Features - Use the root words as features to indicate the
        positiveness or negativeness}
    \item{Classifier - Train a classifier to predict positivity}

  \end{enumerate}
\end{enumerate}
\paragraph{Implications or significance of the problem}
Social Media has been becoming more and more widely used. Accounting to Perrin's
survey, there are only $7\%$ American adults are use social media in 2005.
However, social media usage increase rapily, there are $65\%$ American adults are use
social media untill 2015 \cite{perrin2015social}. In our survey, we also find most of people
are insterest in different language speakers' opinions and attitudes. In
addition,
Most people enounter language and cultureal barriers during cross-language
communication.
As Dr. Haiyun mentions, English language sentiment analysis research has
undergone major developments in recent years \cite{ChineseSentimentAnalysis}.
However, less research has been undertaken in other languages, such as Chinese.
Today, a lot of English language sentiment analysis theories have been
developed. Also, a variety of Machine Translation tools is available, such as Google
translation, Bing translation and Yandex translation.
Manchine Translation uses computational linguistic programs and natural language
processing theory \cite{machineTranslation}.
However, nobody working in a combination of these two fields of research has undertaken non-English
sentiment analysis. Therefore, the research described and discussed in this paper aims to create a testing model to find the best-combination of English
sentiment analysis tools and machine translation tools to obtain reliable
sentiment analysis results from non-English texts, for non-English speakers who
do not have such sentiment analysis tools to analyze their own language.
Eventually, everyone will be able to understand different language speakers'
attitudes (positive or negative), emotions and opinions.\\
\paragraph{Expected Outcomes}

\section{Survey - Questionnaire}\label{survey}

@@

    \item Are you willing to try to understand a comment in an unknown language ?
    \begin{enumerate}
        \item Very likely
        \item Likely
        \item Neither likely nor likely
        \item Unlikely
        \item Very unlikely
    \end{enumerate}
    \textit{Initial Code : Behavior towards unknown languages}
       \item How often do you read others' opinion in social media posts ?
    \begin{enumerate}
        \item Always
        \item Usually
        \item Sometimes
        \item Rarely
        \item Never
    \end{enumerate}
    \textit{Initial Code : Interest in others' opinion}

    \item Which machine translation tool do you mostly use ?
    \begin{enumerate}
        \item Google Translation
        \item Microsoft Bing Translation
        \item Yandex Translation
        \item Baidu Translation
        \item Youdao Translation
        \item Other (please specify)
    \end{enumerate}
    \textit{Initial Code : Types of translation tools}

    \item Sentiment analysis tool can determine the attitude (positive or negative) of writers, which can be useful for analyzing a huge amount of comments. Are you willing to use this tool for analyzing your interest topic in social media, such as product comments or restaurant review, etc?
    \begin{enumerate}
        \item Very likely
        \item Likely
        \item Neither likely nor likely
        \item Unlikely
        \item Very unlikely
    \end{enumerate}
    \textit{Initial Code : Attitude towards sentiment analysis}

\bibliographystyle{IEEEtran}
\bibliography{library}
\end{document}
